\documentclass[l4proj.tex]{subfiles}
\begin{document}    

little blurb 
\section{Software Engineering techniques}
%(~ 2 pages w/ pictures)
A number of different software engineering techniques were implemented during the creation of RViT. An Agile working method was chosen as it suited the project (why?).

Each section of work followed a typical cycle. First a front end design was created, then the relevant API section was designed and updates to the database structure made. The API section was then created and finally the front-end design was implemented. 

\subsection{Sprint-based development}
It was decided to work in sprints during development. This allowed the requirements to be broken into subsections and minimum viable products. Once a sprint had been completed, a new set of issues were proposed as the backlog for the next sprint. While it was time based estimated for different issues were generally accurate, some issues were more difficult due to unforeseen blockers. As the project progressed it was easier to identify what issues would present blockers so more achievable backlogs could be created. 

Any scope creep?

\subsection{Issue tracking}
As this project was carried out in GitHub, issues were created. To understand the issue better, each issue contained a user story, definition of done and was categorised through labels. Why was this helpful?

A kanban board was also created using GitHub projects with four different columns defined. Parking lot, Backlog, In Progress and Done. The Parking lot column was introduced after the first sprint to identify issues that had not yet had a user story or definition of done defined. This was very helpful when new requirements were identified during meetings.

Photo of my kanban board

\subsection{GitHub and Continuous Integration}
both Django and react unit tests integrated into pipeline

Mention that netlify was set up to have continuous integration - especially helpful when ironing out display issues on different size screens

\subsection{Refactoring Code base}
Halfway through the project a large code refactor was carried out. It was noticed some code improvements were needed. 
Removed as many of the repeated code sections as possible
Added automated JavaScript linting with eslint
Improved unit tests 
Organised file structure 
simplifying methods and improving readability of code

\section{API/back end}
\subsection{Database design}
could have entity relationship diagram?

\section{Frontend}
\subsection{components}
\subsection{drag and drop}
\subsection{API calls}

\section{Maintainability}

\section{Reliability}

\section{Deployment}
\end{document}